Example gene set analysis: bringing it together

### 2021-11-25 examples.Rmd
bugfix

means <- colMeans(exdat)
medians <- colMedians(exdat)
sds <- sd(exdat)
summstats <- rbind(means,medians,sds)
summstats %>% kbl(caption="summary statistics of different enrichment analysis comparisons") %>% kable_paper("hover", full_width = F)

>>>>

means <- colMeans(exdat)
medians <- colMedians(exdat)
sds <- apply(exdat,2,sd)
summstats <- rbind(means,medians,sds)
summstats %>% kbl(caption="summary statistics of different enrichment analysis comparisons") %>% kable_paper("hover", full_width = F)
